Prefetching SPARQL query cacher

### 2016-05-10 dissertation/cache-proxy.tex
mention number of Debian packages

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. As
such, it builds on the code of hundreds of authors, too long to
enumerate. I shall constrain myself to list the modules that have code
that has been motivated from this study. Modules that have other
primary authors than myself have been started prior to this present
project, but may have substantial contributions from this project. The
Attean framework was started as part of the effort in
Section~\ref{sec:conpush}, but even though it has been developed
further with the requirements that arose from this project and has
contributions from me, the vast majority of the code has been written
my Gregory Todd Williams. The main work in this project has gone into
the module AtteanX::Query::Cache, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{see \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

@@

>>>>

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. To
install the system on the top of a Debian base system requires 146
Debian packages. As such, it builds on the code of hundreds of
authors, too long to enumerate. I shall constrain myself to list the
modules that have code that has been motivated from this
study. Modules that have other primary authors than myself have been
started prior to this present project, but may have substantial
contributions from this project. The Attean framework was started as
part of the effort in Section~\ref{sec:conpush}, but even though it
has been developed further with the requirements that arose from this
project and has contributions from me, the vast majority of the code
has been written my Gregory Todd Williams. The main work in this
project has gone into the module AtteanX::Query::Cache, where I have
authored the vast majority of the code. The relative difference in
authorship can be further examined by checking the linked Github
repositories, or by using git2prov\footnote{see
  \url{http://git2prov.org/}} to create RDF data of the commit
history. Table~\ref{tab:modules} shows the modules that have been
influenced or written as part of this project.

@@

\subsection{The Attean framework}
